\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
Another one

\PARAGRAPH{Data gathering}
%
Beyond encouraging conferences to trim their emissions, public 
accounting will generate useful data for future organizers.  To this end,
emissions data should be published both in aggregate 
form (total and per-participant footprints), for quick reference, and in raw
form, with an anonymized record for each participant in each
conference, including their originating city.  The data should be made
available in 
a central place, in a uniform format.  Most
conferences' footprints will be dominated by participants' air travel, but the
data gathered should go beyond this to include air travel to in-person PC
meetings and estimated hotel and food {\COtwoE} footprints.

>>>>

\PARAGRAPH{Data gathering}
%
Beyond encouraging conferences to trim their emissions, public 
accounting will generate useful data for future organizers.  \mwh{CUT: To this end,
emissions data should be published both in aggregate 
form (total and per-participant footprints), for quick reference, and in raw
form, with an anonymized record for each participant in each
conference, including their originating city.}  The data should be made
available in 
a central place, in a uniform format.  Most
conferences' footprints will be dominated by participants' air travel, but the
data gathered should go beyond this to include air travel to in-person PC
meetings and estimated hotel and food {\COtwoE} footprints.
